Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
copyedit acks

The authors and contributors acknowledge active support from INRIA. Past and
present sponsors of the project also include Google for funding code
scholarships (\textit{Google Summer of Code}),
the Python Software Fundation and Tinyclues for funding coding sprints.

>>>>

The authors and contributors acknowledge active support from INRIA. Past and
present sponsors of the project also include Google for funding
scholarships through its Summer of Code program,
the Python Software Fundation and Tinyclues for funding coding sprints.
